Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-23 Draft.Rmd
Update Draft.Rmd

3. There is interest in developing more cost-effect approaches to monitoring air pollution
on the ground. Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD. How well do
CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction performance of your model change when CMAQ or aod are included (or not included) in
the model?

4. The dataset here did not include data from Alaska or Hawaii. Do you think your model
will perform well or not in those two states? Explain your reasoning

>>>>

3. There is interest in developing more cost-effect approaches to monitoring air pollution
on the ground. Two candidates for replacing the use of ground-based monitors are numerical models like CMAQ and satellite-based observations such as AOD. How well do
CMAQ and AOD predict ground-level concentrations of PM2.5? How does the prediction performance of your model change when CMAQ or aod are included (or not included) in
the model?
- create visualization showing how close features CMAQ and AOD predict values of PM2.5 to actual/observed values

4. The dataset here did not include data from Alaska or Hawaii. Do you think your model
will perform well or not in those two states? Explain your reasoning
Given that the top 10 features were 'CMAQ,' 'lat,' 'county_area,' 'lon,' 'aod,' 'popdens_county,' 'zcta,' 'log_nei_2008_pm25_sum_10000,' 'fips,' and 'log_nei_2008_pm10_sum_10000,' we think that XG Boost model will perform well since the origin dataset included states of varying sizes and pollution levels. Moreover, its RMSE score is .42 and R^2 is .98, indicating that the prediction performance of this model is excellent. Since Hawaii and Alaska are almost polar opposites with the former being geographically smaller and having hotter climate, we suspect that the model will be able to predict PM2.5 concentration levels in Hawaii and Alaska if they were included in this dataset since the diversity but also interrelatedness in this dataset aids the model in learning the different environments in which pollution occurs.
